---
theme-settings:
  theme: flatly
---

```{r}
library(surveydown)
```

--- welcome

# Movie Preferences Survey

Welcome! This brief survey asks about your movie watching habits.

```{r}
sd_question(
  type = "text",
  id = "name",
  label = "What is your first name?"
)
```

--- honeypot

## Your Viewing Habits

```{r}
# Hidden honeypot question 
sd_question(
  type = "text",
  id = "favorite_director",
  label = "Who is your favorite film director?"
)
```

```{r}
# Time-based trap - this page should take at least 3 seconds to read
sd_question(
  type = "mc",
  id = "movie_frequency",
  label = "How often do you watch movies?",
  option = c(
    "Daily" = "daily",
    "Weekly" = "weekly", 
    "Monthly" = "monthly",
    "Rarely" = "rarely",
    "Never" = "never"
  )
)
```

```{r}
# Fake option trap
sd_question(
  type = "mc_multiple",
  id = "streaming_services",
  label = "Which streaming services do you use? (Select all that apply)",
  option = c(
    "Netflix" = "netflix",
    "Hulu" = "hulu",
    "Disney+" = "disney",
    "Amazon Prime" = "prime",
    "HBO Max" = "hbo",
    "MovieStream Pro" = "fake_service",  # Fake service
    "None" = "none"
  )
)
```

--- consistency

## Movie Knowledge

```{r}
# Ask about a non-existent movie
sd_question(
  type = "mc",
  id = "fake_movie",
  label = "Have you seen the movie 'The Crimson Eclipse' (2019)?",
  option = c(
    "Yes, I've seen it" = "yes",
    "No, I haven't seen it" = "no",
    "I'm not sure" = "unsure"
  )
)
```

```{r}
# Simple math CAPTCHA alternative
sd_question(
  type = "numeric",
  id = "simple_math",
  label = "Please solve: What is 7 + 5?"
)
```

```{r}
# Reversed scale trap
sd_question(
  type = "slider",
  id = "movie_enjoyment",
  label = "On a scale from LOVE to HATE, how do you feel about movies in general?",
  option = c(
    "Hate" = "hate",
    "Dislike" = "dislike", 
    "Neutral" = "neutral",
    "Like" = "like",
    "Love" = "love"
  )
)
```

--- attention_check_page

## Your Preferences

Please read carefully: **For this question only, please select "Action" regardless of your actual preference.**

```{r}
sd_question(
  type = "mc",
  id = "attention_check",
  label = "What is your favorite movie genre?",
  option = c(
    "Comedy" = "comedy",
    "Drama" = "drama",
    "Action" = "action",
    "Horror" = "horror",
    "Romance" = "romance",
    "Sci-Fi" = "scifi"
  )
)
```

```{r}
# Consistency check - same question worded differently
sd_question(
  type = "mc",
  id = "movie_frequency_check",
  label = "In a typical month, how many times do you watch a movie?",
  option = c(
    "More than 20 times" = "daily_equivalent",
    "5-20 times" = "weekly_equivalent",
    "1-4 times" = "monthly_equivalent", 
    "Less than once" = "rarely_equivalent",
    "I don't watch movies" = "never_equivalent"
  )
)
```

--- logic_trap

## Final Questions

```{r}
# Impossible combination question
sd_question(
  type = "mc",
  id = "movie_year",
  label = "When did you last watch a movie in theaters?",
  option = c(
    "In the past week" = "week",
    "In the past month" = "month",
    "In the past year" = "year",
    "More than a year ago" = "year_plus",
    "Never been to a theater" = "never"
  )
)
```

```{r}
# Response time will be tracked for this text question
sd_question(
  type = "textarea",
  id = "movie_description",
  label = "In your own words, briefly describe your most memorable movie theater experience:",
  height = "100px"
)
```

--- complete

## Thank You!

Your code is: `r sd_output("completion_code", type = "value")`

Please save this code for your records.

```{r}
sd_close()
```
